---
title: "Analysis on main sample"
author: "Erik Ø. Sørensen"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
library(targets)
library(tidyverse)
library(gt)
library(modelsummary)
library(scales)
library(patchwork)
library(fixest)
source(here::here("code", "functions.R"))
```


# Balance table

```{r balance, echo=FALSE, message=FALSE, warning=FALSE}
tar_load(balance_2018)
btable <- balance_2018 |>
  gt() |> 
  fmt_number(decimals = 3) |> 
  fmt_number(decimals=1, rows=1, columns = 2:6) |>
  tab_spanner(label="Winner-Take-All treatments", columns=3:5)
btable
btable |> gtsave(here::here("tables","RN2018_balance.tex"))
```


# Share of earnings given to winner

```{r Share of earnings given to winner, echo=FALSE}
tar_load(share_of_earnings_to_winner)
share_of_earnings_to_winner
ggsave("graphs/RN2018_hist_shareY_wta.pdf",width=16, height = 10, units = "cm")
```


Here are corresponding numbers. Sometimes equalizing is difficult in monetary units. 
For equalize in this table, I allow the difference between implemented amounts and
equal amounts to be less than 10 cent.
```{r echo=FALSE}
tar_load(mmw2018)
mmw2018 |> group_by(treatment) |>
  summarize(winner_take_all = mean(y2==e2),
            equalize = mean(abs(y2- e2/2 )<0.10),
            mean_to_winner = mean(y2/e2)) |>
  gt() |>
  fmt_number(decimals=3)

```



# Share given to winner and loser


Just overall share to winner in all WTA pooled:

```{r}
mmw2018 |> filter(treatment!="Base") |>
  summarize(mean_share_to_winner_WTA_pooled = mean(y2/e2),
            n = n()) |>
  gt() |> fmt_number(decimals=3)
```


Sometimes, spectators gave the loser more than the winner. Here is a distribution
of amounts to winner and loser in WTA and Luck treatments

```{r}
mmw2018 |>   mutate(wta = treatment!="Base",
                    y_cat = if_else(y2==0,
                                    "0",
                                    as.character(cut(
                                      y2/e2,
                                      breaks = c(0, 0.5, Inf),
                                      labels = c("(0,0.5)", "[0.5,1]"),
                                      right = FALSE)
                                      )),
                    outcome = factor(y_cat, levels=c("0","(0,0.5)","[0.5,1]"))) |>
  
  count(treatment, outcome) %>%
  group_by(treatment) %>%
  mutate(share = n / sum(n)) %>%
  ungroup() |> gt() |> fmt_number(decimals = 3, columns = 4)
```

Share in WTA that has $y_1\geq y_2+0.1$ and equality at $|y_1-y_2|<0.1$:
```{r}
mmw2018 |> mutate(y1_10c_or_more_than_winner = (y1 >= y2+1),
                  equality = abs(y1-y2)<0.1) |>
  group_by(treatment) |>
  summarize(share_y1_10c_or_more_than_winner = mean(y1_10c_or_more_than_winner),
            share_equality = mean(equality)) |>
  gt() |> fmt_number(decimals = 3)

```


# Winner-take-all vs. Luck

```{r Winner-take-all vs luck, echo=FALSE}
tar_load(winner_take_all_vs_luck)
winner_take_all_vs_luck$left + winner_take_all_vs_luck$right + plot_annotation(tag_levels = "a") + plot_layout(guides = "collect")
ggsave("graphs/RN2018_wta_luck.pdf", width=16, height = 10, units="cm")
```


# Role of winning margin

```{r Role of winning margin, echo=FALSE}
tar_load(role_of_winning_margin_graph)
role_of_winning_margin_graph$top / role_of_winning_margin_graph$bottom + plot_annotation(tag_levels = "a")
ggsave("graphs/RN2018_flatness1_version2.pdf", width=16, height = 12, units="cm", device=cairo_pdf)
```





# Heterogeneity Analysis: All to winner and share to winner


Putting these together:
```{r heterogeneity analysis I, echo=FALSE}
tar_load(heterogeneity_figure_all_to_winner)
g <- heterogeneity_figure_all_to_winner
g$g11 + g$g12 + g$g21 + g$g22 + plot_annotation(tag_level="a")
ggsave("graphs/RN2018_hetero_coefplot.pdf", width=16, height=12, units="cm")
```

And the numbers in upper left corner:
```{r}
het11(mmw2018)$all_data |> gt() |> fmt_number(decimals=3)
```




```{r heterogeneity analysis II, echo=FALSE}
tar_load(heterogeneity_figure_share)
h <- heterogeneity_figure_share
h$g11 + h$g12 + h$g21 + h$g22 + plot_annotation(tag_level="a")
ggsave("graphs/RN2018_hetero_coefplot_s.pdf", width=16, height=12, units="cm")
```


And the numbers in upper left corner:
```{r}
het11(mmw2018)$share_data |> gt() |> fmt_number(decimals=3)
```

# Heterogeneity between competition treatments

```{r heterogeneity between treatments}
GL <- tar_read(heterogeneous_subtreatment_effects_gg)
GL$g11 + GL$g12 + GL$g21 + GL$g22 + plot_annotation(tag_levels="a")
ggsave("graphs/RN2018_subtreatment_heterogeneity.pdf", width=16, heigh=12, units="cm")
```



# Questionnaire responses
Important to remeber that the Gold medalist and Steven Spielberg questions must be scale reversed
to fit graph.

```{r wuestionnaire responses, echo=FALSE}
tar_load(question_responses)
n <- question_responses
n$a + n$b + n$c + plot_annotation(tag_levels = "a")
ggsave("graphs/RN2018_attitudes_hist.pdf", width=16, height = 10, units="cm", device = cairo_pdf)
```

Numbers of agreement with Gold medalists: 

```{r}
tar_load(mmw2018)
mean( (8-mmw2018$att3)>4)
```

Numbers of agreement with Steven Spielberg ...
```{r}
mean( (8-mmw2018$att4)>4)
```
Taxes on top 1 percent should stay the same or decrease
```{r}
mean( (mmw2018$att2)>1)
```
Correlations (Spearman) between Gold Medalist and Steven Spielberg question:

```{r}
cor.test(8-mmw2018$att3, 8-mmw2018$att4, method="spearman")
```

Correlations (Spearman) between Gold Medalist and income taxation question:

```{r}
cor.test(8-mmw2018$att3, mmw2018$att2, method="spearman")
```
Correlations (Spearman) between Steven Spielberg and income taxation question:

```{r}
cor.test(8-mmw2018$att4, mmw2018$att2, method="spearman")
```


# Performance of workers by treatment

```{r distributions I, echo=FALSE}
tar_load("distribution_of_performance_by_treatment")
X <- distribution_of_performance_by_treatment
X$a + X$b + X$c + X$d + plot_annotation(tag_levels = "a")
ggsave("graphs/RN2018_distribution_levels.pdf", width=16, height=10, units="cm", device=cairo_pdf)
```

```{r distributions II, echo=FALSE}
tar_load("distribution_of_winning_margin_by_treatment")
Y <- distribution_of_winning_margin_by_treatment
Y$a + Y$b + Y$c + Y$d + plot_annotation(tag_levels="a")
ggsave("graphs/RN2018_distribution_margins.pdf", width=16, height=10, units="cm", device=cairo_pdf)
```


# Role of winning margin by treatment

```{r role of winning margin take-all, echo=FALSE}
tar_load("flatness_all_to_winner")
flatness_all_to_winner
ggsave("graphs/RN2018_flatness_all_byT.pdf", width=16, height = 14, units="cm", device=cairo_pdf)
```

```{r role of winning margin share, echo=FALSE}
tar_load("flatness_share_to_winner")
flatness_share_to_winner
ggsave("graphs/RN2018_flatness_share_byT.pdf", width=16, height=14, units="cm", device=cairo_pdf)
```




# Regression analysis: The role of merit for inequality acceptance

```{r role of merit for inqeuality acceptance, echo=FALSE}
tar_load(role_of_merit_table)

cm <- c("competition" = "WTA Competition",
        "republican" = "Republican",
        "college" = "College",
        "female" = "Female",
        "above_median_age" = "Above median age",
        "(Intercept)"="Constant"
        )
tab2 <- role_of_merit_table |>
  modelsummary(coef_map=cm,
               stars = c('*' = .1, '**' = .05, '***'=.01),
                                   gof_map = c("nobs", "r.squared"),
                                   output = "gt") |>
  tab_spanner(label="All to Winner", columns=2:5) |>
  tab_spanner(label="Share to Winner", columns=6:9)
tab2
tab2 |> gtsave(here::here("tables","RN2018_role_of_merit.tex"))
```

# Regression Analysis: The Role of the Winning Margin for Inequality Acceptance

```{r role of margin for inqeuality acceptance, echo=FALSE}
tar_load(role_of_winning_margin)
dm <- c("winning_margin" = "Winning margin",
        "republican" = "Republican",
        "college" = "College",
        "female" = "Female",
        "above_median_age" = "Above median age",
        "performance_winner" = "Performance winner",
        "(Intercept)"="Constant"
        )
tab3 <- role_of_winning_margin |>
  modelsummary(coef_map=dm,
               stars = c('*' = .1, '**' = .05, '***'=.01),
                                   gof_map = c("nobs", "r.squared"),
                                   output = "gt") |>
  tab_spanner(label="All to Winner", columns=2:4) |>
  tab_spanner(label="Share to Winner", columns=5:7)
tab3
tab3 |> gtsave(here::here("tables","RN2018_role_of_margin.tex"))
```

# Regression analysis: Association between giving all to the winner and general attitudes

```{r general attitudes, echo=FALSE}
tar_load(ass_giving_all_attitudes)
em <- c("all_to_winner" = "All to winner",
        "share_to_winner" = "Share to winner",
        "republican" = "Republican",
        "college" ="College",
        "female" = "Female",
        "above_median_age"="Above median age",
        "(Intercept)"="Constant"
)
t4_2018 <- ass_giving_all_attitudes$all_to_winner |>
   modelsummary(coef_map=em,
               stars = c('*' = .1, '**' = .05, '***'=.01),
                                   gof_map = c("nobs", "r.squared"),
                                   output = "gt" ) |>
  tab_spanner(label="Gold medalist", columns=2:4) |>
  tab_spanner(label="Superstar", columns=5:7) |>
  tab_spanner(label="Decrease tax on top 1\\%", columns=8:10)
t4_2018
t4_2018 |> gtsave(here::here("tables","RN2018_attitudes.tex"))
```

What is the explained variation of taxes on the top 1% on
just voting republicant?

```{r}
tar_load(mmw2018)
df <- mmw2018 |> mutate(republican = as.numeric(pol2==1)) |> filter(treatment!="Base")
lm(scale(att2) ~ republican, data=df) |> summary()
```



# Regression analysis: Association between share to the winner and general attitudes

```{r}
tar_load(ass_giving_all_attitudes)
em <- c("all_to_winner" = "All to winner",
        "share_to_winner" = "Share to winner",
        "republican" = "Republican",
        "college" ="College",
        "female" = "Female",
        "above_median_age"="Above median age",
        "(Intercept)"="Constant"
)
u4_2018 <- ass_giving_all_attitudes$share_to_winner |>
   modelsummary(coef_map=em,
               stars = c('*' = .1, '**' = .05, '***'=.01),
                                   gof_map = c("nobs", "r.squared"),
                                   output = "gt" ) |>
  tab_spanner(label="Gold medalist", columns=2:4) |>
  tab_spanner(label="Superstar", columns=5:7) |>
  tab_spanner(label="Decrease tax on top 1\\%", columns=8:10)
u4_2018
u4_2018 |> gtsave(here::here("tables","RN2018_attitudes_share.tex"))

```





# Regression analysis: Comparison of winner-take-all treatments

```{r comparisons of treatments, echo=FALSE}
tar_load(mmw2018)
tabledf <- mmw2018 |>
  filter(treatment!="Base") |>
  mutate(all_to_winner = as.numeric(y2==e2),
         share_to_winner = y2/(y1+y2),
         winning_margin = x2-x1,
         republican = as.numeric(pol2==1),
         college = as.numeric(education>4),
         female = as.numeric(sex==2),
         above_median_age = as.numeric(age > median(age)),
         regionf = factor(area),
         performance_winner = x2,
         treatment = fct_relevel(treatment, "WTA")
         )

f1 <- tabledf |> feols(all_to_winner ~ treatment, data=_, vcov="hetero")
f1p <- wald(f1, c("treatmentWTA: No Choice", "treatmentWTA: No Exp"))$p
f2 <- tabledf |> feols(all_to_winner ~ treatment + republican + college + female + above_median_age  | regionf, data=_, vcov="hetero")
f2p <- wald(f2, c("treatmentWTA: No Choice", "treatmentWTA: No Exp"))$p
f3 <- tabledf |> feols(all_to_winner ~ treatment + republican + college + female + above_median_age + performance_winner | regionf, data=_, vcov="hetero")
f3p <- wald(f3, c("treatmentWTA: No Choice", "treatmentWTA: No Exp"))$p
f4 <- tabledf |> feols(share_to_winner ~ treatment, data=_)
f4p <- wald(f4, c("treatmentWTA: No Choice", "treatmentWTA: No Exp"))$p
f5 <- tabledf |> feols(share_to_winner ~ treatment + republican + college + female + above_median_age  | regionf, data=_, vcov="hetero")
f5p <- wald(f5, c("treatmentWTA: No Choice", "treatmentWTA: No Exp"))$p
f6 <- tabledf |> feols(share_to_winner ~ treatment + republican + college + female + above_median_age + performance_winner | regionf, data=_, vcov="hetero")
f6p <- wald(f6, c("treatmentWTA: No Choice", "treatmentWTA: No Exp"))$p
fextra_rows <- tibble(p0 = c("$P$(all treatments equal)"),
                     p1 = f1p,
                     p2 = f2p,
                     p3 = f3p,
                     p4 = f4p,
                     p5 = f5p,
                     p6 = f6p)

fm <- c("treatmentWTA: No Choice" = "WTA-No Choice",
        "treatmentWTA: No Exp" = "WTA-No Exp.",
        "republican" = "Republican",
        "college" ="College",
        "female" = "Female",
        "above_median_age"="Above median age",
        "performance_winner"="Performance winner",
        "(Intercept)"="Constant"
)

ta2 <- list(f1,f2,f3,f4,f5,f6) |>
   modelsummary(coef_map=fm,
               stars = c('*' = .1, '**' = .05, '***'=.01),
                                   gof_map = c("nobs", "r.squared"),
                                   output = "gt" ,
               add_rows = fextra_rows) |>
  tab_spanner(label="All to winner", columns=2:4) |>
  tab_spanner(label="Share to winner", columns=5:7) 
ta2
ta2 |> gtsave(here::here("tables","RN2018_T_comparisons.tex"))
```


# Outcomes on background variables

```{r outcomes on background, echo=FALSE, message=FALSE, warning=FALSE}
tar_load(outcomes_on_background)
oob <- outcomes_on_background$regs |> 
   modelsummary(coef_map=outcomes_on_background$names,
               stars = c('*' = .1, '**' = .05, '***'=.01),
                                   gof_map = c("nobs", "r.squared"),
                                   output = "gt") |>
  tab_spanner(label="Full sample", columns = 2, id=101) |>
  tab_spanner(label="Smallest margin", columns = 3, id=102) |>
  tab_spanner(label="Full sample", columns = 4, id=103) |>
  tab_spanner(label="Smallest margin", columns = 5, id=104) |>
  tab_spanner(label="All to winner", columns=2:3) |>
  tab_spanner(label="Share to winner", columns=4:5) 
oob
oob |> gtsave(here::here("tables","RN2018_outcomes_on_background.tex"))
```

Also included but not reported: Census area FE. 


# Heterogeneous treatment effects of the role of merit for inequlity acceptance: All to winner

```{r heterogeneous merit all, echo=FALSE}
tar_load(heterogeneous_treatment_effects_all)
qm <- c("competition"="WTA Competition",
        "competition:republican" = "WTA Competition $\\times$ Republican",
        "competition:college" = "WTA Competition $\\times$ College",
        "competition:female" = "WTA Competition $\\times$ Female",
        "competition:above_median_age"= "WTA Competition $\\times$ Above median age")
ta3 <- heterogeneous_treatment_effects_all$regressions |>
  modelsummary(coef_map=qm,
               stars = c('*' = .1, '**' = .05, '***'=.01),
                                   gof_map = c("nobs", "r.squared"),
                                   output = "gt",
               add_rows = heterogeneous_treatment_effects_all$extra_rows) |>
  tab_spanner(label="Full sample", columns=2:5) |>
  tab_spanner(label="Smallest winning margin", columns=6:9)
ta3
ta3 |> gtsave(here::here("tables","RN2018_hetmerit_all.tex"))
```




# Heterogeneous treatment effects of the role of merit for inequlity acceptance: Share to winner

```{r heterogeneous merit share, echo=FALSE}
tar_load(heterogeneous_treatment_effects_share)
qm <- c("competition"="WTA Competition",
        "competition:republican" = "WTA Competition $\\times$ Republican",
        "competition:college" = "WTA Competition $\\times$ College",
        "competition:female" = "WTA Competition $\\times$ Female",
        "competition:above_median_age"= "WTA Competition $\\times$ Above median age")
ta4 <- heterogeneous_treatment_effects_share$regressions |>
  modelsummary(coef_map=qm,
               stars = c('*' = .1, '**' = .05, '***'=.01),
                                   gof_map = c("nobs", "r.squared"),
                                   output = "gt",
               add_rows = heterogeneous_treatment_effects_share$extra_rows) |>
  tab_spanner(label="Full sample", columns=2:5) |>
  tab_spanner(label="Smallest winning margin", columns=6:9)
ta4
ta4 |> gtsave(here::here("tables","RN2018_hetmerit_share.tex"))
```

# Heterogeneous treatment effects of the role of the winning margin

```{r heterogeneous merit margin, echo=FALSE}
tar_load(heterogeneous_treatment_effects_wm)
qm <- c("winning_margin"="Winning margin",
        "winning_margin:republican" = "Winning margin $\\times$ Republican",
        "winning_margin:college" = "Winning margin $\\times$ College",
        "winning_margin:female" = "Winning margin $\\times$ Female",
        "winning_margin:above_median_age"= "Winning margin $\\times$ Above median age")
ta5 <- heterogeneous_treatment_effects_wm$regressions |>
  modelsummary(coef_map=qm,
               stars = c('*' = .1, '**' = .05, '***'=.01),
                                   gof_map = c("nobs", "r.squared"),
                                   output = "gt",
               add_rows = heterogeneous_treatment_effects_wm$extra_rows) |>
  tab_spanner(label="All to winner", columns=2:5) |>
  tab_spanner(label="Share to winner", columns=6:9)
ta5
ta5 |> gtsave(here::here("tables","RN2018_hetmerit_margin.tex"))
```

# Median age

```{r}
tar_load(mmw2018)
median(mmw2018$age)
```

